finalproj

### 2022-04-21 initialdraft.Rmd
added GDP source link
added hours worked data

@@

#Starting to mess with hours worked but realized that missing data is going to be a problem
```{r}
ggplot(healthy_data_2, aes(y = fct_reorder(City, `Annual avg. hours worked`), x = `Annual avg. hours worked`, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "",
       caption = "Data from: ADD LATER",
       x = "",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() 
```

>>>>

[GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)

@@

#Starting to mess with hours worked but realized that missing data is going to be a problem
```{r}
ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "",
       caption = "Data from: ADD LATER",
       x = "",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() 
```
